---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# launcheR

The goal of launcheR is to easily launch R scripts with 2 available features :

1. Waiting queue management
    * `queue` can belong to a group. A group can run only one queue at once.
    * A `batch` can be parallelizable among all groups or not
    * *"first come, first served"*, then `queue` or `batch` are set in a waiting queue and launch ASAP.
2. Easy set of parameters
    * No more trouble with `args` in `Rscript`
    * All class can be set as parameters

**NB : ** `Rscript` is run in background, you get your prompt back `r emo::ji("smile")`


## Installation

You can install launcheR from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("qfazille/launcheR")
```

The management of waiting queue & waiting batch can be shared by multiple users if you all use the same machine.


## Basic example

This creates a queue containing 2 batchs

```{r basic_example, eval = FALSE}
library(launcheR)

# create queue
q <- queue()

# Add batchs script1.R & script2.R
q <- add.batch(queue = q, path = "/path/to/script1.R")
q <- add.batch(queue = q, path = "/path/to/script2.R")

# launch queue
launch.queue(q)
```

## Using arguments on a batch

Add a batch with arguments (parameters)

````{r args_example, eval = FALSE}
# Some random values in params list (must be named)
username <- "mylogin"
country <- "france"
age <- 99
other <- list(a = 1, b = "hello", d = "world")

# params must be a named list
params <- list(username = username, country = country, age = age, other = other)

# Add batch script1.R with those parameters
q <- add.batch(queue = q, path = "/path/to/script1.R", params = params)

````

## Launch queue on same group

**NB : ** Both users are on the same machine

**user1**
````{r group_example, eval = FALSE}
library(launcheR)

# create queue on group 'demo'
q <- queue(group = "demo")

# Add batchs script1.R & script2.R
q <- add.batch(queue = q, path = "./script1.R")
q <- add.batch(queue = q, path = "./script2.R")

# Launch
launch.queue(q)
````

**user2**
````{r group_example2, eval = FALSE}
library(launcheR)

# create queue on group 'demo'
q <- queue(group = "demo")

# Add batchs script1.R & script3.R
q <- add.batch(queue = q, path = "./script1.R")
q <- add.batch(queue = q, path = "./script3.R")

# Launch
launch.queue(q)
````


